Calendar-based graphics for visualising people's daily schedules

### 2017-07-06 main.Rmd
refine section 2.3

Grouping the cells according to the common days give rise to these scales. The minimums and maximums computed for every $(i, j)$ together with every $(m, n)$ allow for individual scale over all the single days. Similarly, $j$ indexing day of the week is bundled to determine the scales on days of a week, and $g$ representing the day in the month is for the scales on days of a month.

@@

It can be noted that reference lines separating each cell and panel and labels indicating weekday and month are also constructed in order to make calendar-based graphics more accessible and informative.

Regarding the monthly calendar format, the major reference lines separate every month panel and the minor ones separate every day cell, represented by the think and thin lines respectively. The major reference lines are placed on the far left and right as well as the bottom and top of every month panel: for each $m$, the vertical lines are determined by $\min{(x)}$ and $\max{(x)}$; for each $n$, the horizontal lines are computed by $\min{(y)}$ and $\max{(y)}$. The minor reference lines are placed on the initial positions: for each $i$, the vertical line is $\min{(x)}$; for each $j$, the horizontal line is $\min{(y)}$.

The abbreviated month labels located on the top left are obtained through $(\min{(x)}, \max{(y)})$ for every $m$ and $n$. The weekday texts with a single letter are uniformly placed on the bottom of the whole canvas, that is $\min{(y)}$.

@@

We shall enable interactivity in the calendar-based graphics for time series data. It will allow users to transform different temporal components and switch displays between overlaying and faceting through key strokes or mouse clicks.

>>>>

Grouping the cells according to the common period give rise to these scales. The minimums and maximums obtained for every $(i, j)$ and $(m, n)$ allow for individual scale over all the single days. Similarly, $j$ indexing day of the week is bundled to determine the scales on days of a week, and $g$ representing the day in the month is for the scales on days of a month.

@@

Reference lines dividing each cell and block as well as labels indicating weekday and month are also provided in order to make calendar-based graphics more accessible and informative.

Regarding the monthly calendar, the major reference lines separate every month panel and the minor ones separate every cell, represented by the think and thin lines respectively. The major reference lines are placed surrounding every month block: for each $m$, the vertical lines are determined by $\min{(x)}$ and $\max{(x)}$; for each $n$, the horizontal lines are given by $\min{(y)}$ and $\max{(y)}$. The minor reference lines are placed on the left side of every cell: for each $i$, the vertical division is $\min{(x)}$; for each $j$, the horizontal is $\min{(y)}$.

The abbreviated month labels located on the top left are obtained through $(\min{(x)}, \max{(y)})$ for every $m$ and $n$. The weekday texts with a single letter are uniformly placed on the bottom of the whole canvas, that is $\min{(y)}$, with the central position of a cell $x / 2$ for each $j$.

@@

### 2017-07-06 main.tex
refine section 2.3

Grouping the cells according to the common days give rise to these
scales. The minimums and maximums computed for every \((i, j)\) together
with every \((m, n)\) allow for individual scale over all the single
days. Similarly, \(j\) indexing day of the week is bundled to determine
the scales on days of a week, and \(g\) representing the day in the
month is for the scales on days of a month.

@@

It can be noted that reference lines separating each cell and panel and
labels indicating weekday and month are also constructed in order to
make calendar-based graphics more accessible and informative.

Regarding the monthly calendar format, the major reference lines
separate every month panel and the minor ones separate every day cell,
represented by the think and thin lines respectively. The major
reference lines are placed on the far left and right as well as the
bottom and top of every month panel: for each \(m\), the vertical lines
are determined by \(\min{(x)}\) and \(\max{(x)}\); for each \(n\), the
horizontal lines are computed by \(\min{(y)}\) and \(\max{(y)}\). The
minor reference lines are placed on the initial positions: for each
\(i\), the vertical line is \(\min{(x)}\); for each \(j\), the
horizontal line is \(\min{(y)}\).

The abbreviated month labels located on the top left are obtained
through \((\min{(x)}, \max{(y)})\) for every \(m\) and \(n\). The
weekday texts with a single letter are uniformly placed on the bottom of
the whole canvas, that is \(\min{(y)}\).

>>>>

Grouping the cells according to the common period give rise to these
scales. The minimums and maximums obtained for every \((i, j)\) and
\((m, n)\) allow for individual scale over all the single days.
Similarly, \(j\) indexing day of the week is bundled to determine the
scales on days of a week, and \(g\) representing the day in the month is
for the scales on days of a month.

@@

Reference lines dividing each cell and block as well as labels
indicating weekday and month are also provided in order to make
calendar-based graphics more accessible and informative.

Regarding the monthly calendar, the major reference lines separate every
month panel and the minor ones separate every cell, represented by the
think and thin lines respectively. The major reference lines are placed
surrounding every month block: for each \(m\), the vertical lines are
determined by \(\min{(x)}\) and \(\max{(x)}\); for each \(n\), the
horizontal lines are given by \(\min{(y)}\) and \(\max{(y)}\). The minor
reference lines are placed on the left side of every cell: for each
\(i\), the vertical division is \(\min{(x)}\); for each \(j\), the
horizontal is \(\min{(y)}\).

The abbreviated month labels located on the top left are obtained
through \((\min{(x)}, \max{(y)})\) for every \(m\) and \(n\). The
weekday texts with a single letter are uniformly placed on the bottom of
the whole canvas, that is \(\min{(y)}\), with the central position of a
cell \(x / 2\) for each \(j\).
